---
title: "ETFs in laboratory asset markets"
author: J. Duffy, JP Rabanal, O Rud, 

output: revealjs::revealjs_presentation
---

## Research question

- Does the ETFs affect price discovery? 

## Market Design

- 3 assets: A, B and C, where $C= A + B$
- T = 15 periods
- dividend streams: 
  - A pays 1 or -1 
  - B pays the opposite of A in all periods. Starting from t=8, pays plus 1. 
- FVs
  - $FV_{{A,t}}= 10$
  - $FV_{B,t}=\left\{\begin{array}{ll} 180 & \mbox{for}\ t \leq 8 \\
            (T-t+1)10 + 100 & \mbox{for}\ t > 8
            \end{array} \right.$
  - $FV_{C,t}=\left\{\begin{array}{ll} 280 & \mbox{for}\ t \leq 8 \\
            (T-t+1)10 + 200 & \mbox{for}\ t > 8
            \end{array} \right.$

## Experimental Design

- Each market, 9 players
- Endowments of (A,B,C,cash)
  - 

## Market prices

```{r,echo=FALSE}
source("/cloud/project/project/getdata.R")
plot(df$subsession.round_number,df$group.p_c,ylim=c(0,100),col="blue",xaxt = "n",xlab="period",ylab = "prices")
axis(1, at=c(1:15,18:32), labels=c(1:15,1:15))
lines(df$subsession.round_number,df$group.nav,col="blue")
points(df$subsession.round_number,df$group.p_a,col="gray",pch=2)
#lines(df$subsession.round_number,df$group.nav_a,col="black")
points(df$subsession.round_number,df$group.p_b,col="red",pch=3)
#lines(df$subsession.round_number,df$group.nav_b,col="red")
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

