---
title: "ETFs "
output: html_notebook
---

Here's a description about the results of session 10/24. 

* Prices of A, B and C above FV. 

* It's puzzling to see the high price of A and B compared to FV. 

* $p_A$ is double the price of FV. A risk aversion story falls short in explaining this behavior. 

* the price gap btw $p_B-p_A$ tends to stabilize around 11.0 in first stage for round 2. 

* what's the role of C? If a investor is holding $C$ then she should realize that it's value is way higher compared to the two underlying assets. it should sell it. but what happen if you hold it and A and B are way to overprice... so just keep it then!

* perhaps, we should endow every player with at least some $C$. 

* new endowments

  * type I : 6 2 2 
  * type II: 2 6 2 
  * type III: 2 2 6
  
* in a simple environment 

$$
u(c)
$$


$$
c + p x = w
$$  
We solve this backwards, so starting at time $T$, we have utility of holding A is 
$$
.5 \times u(11) + .5 \times u(9) 
$$
Assuming CARA


```{r}
ut<-function(g,x){
x^(1-g)/(1-g)
}
g<-0.7
eu<- 0.5*ut(g,11)+0.5*ut(g,9) # only A 
euab<- 0.5*ut(g,21)+0.5*ut(g,21)
ce <- (eu*(1-g))^(1/(1-g))
ce

```









```{r}
plot(cars)
```

